---
title: "In-class Exercise 4: Interactivity and Statistical Analysis"
author: "Anica Clarice Antonella P. Galano (acapgalano)"
date: 4 February 2023
date-modified: "`r Sys.Date()`"
execute:
  warning: false
format: html
editor: visual
---

## 🔍 Overview

This document serves as my In-class Exercise 4 requirement, following the fourth week of ISSS608 VAA lecture of Professor Kam on February 4, 2023.

## 🌱 Getting Started 

### Installing packages into the R environment

```{r}
pacman::p_load(ggiraph, plotly, DT, patchwork, crosstalk, tidyverse, ggstatsplot)
```

### Loading the data into the R environment

```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

## 🚀 Exploring the **`plotly`** Package

### Creating our first basic plot

```{r}
plot_ly(
  data = exam_data,
  x = ~ENGLISH,
  y = ~MATHS,
  color = ~RACE
)
```

We can observe that by default we are given a tooltip containing the pair of 'ENGLISH' and 'MATHS' scores. More into interactivity, several functions are provided by the new plot at the top right corner.

### Creating an alternative `ggplot` plot with `plotly`

```{r}
p <- ggplot(data = exam_data,
            aes( x = MATHS,
                 y = ENGLISH)) + 
  geom_point(dotsize = 1) + 
  coord_cartesian(xlim = c(0,100),
                  ylim = c(0,100))
ggplotly(p)
```

::: {.callout-note icon="false"}
## 🎓 MORAL OF THE STORY

Use **`ggplot`** if you want to have control over the design, and use **`plotly`** for easier and better interactivity. You can still control the design if you use native **`ggplot`** objects.
:::

## Performing Visual Statistical Analysis Using `ggstatsplot`

```{r}
ggbetweenstats(
  data = exam_data,
  x = GENDER,
  y = MATHS,
  type = "p",
  messages = FALSE
)
```

As shown above we can observe the sample means represented by the red dot and labelled accordingly. We can also observe that Welch test was also performed with a p-value of 0.53. List of statistical tests can be found [here](https://indrajeetpatil.github.io/statsExpressions/ "{statsExpressions}: Tidy dataframes and expressions with statistical details").
