---
title: "In-class Exercise 2: Creating Eelegant Graphics with ggplot2"
author: "Anica Clarice Antonella P. Galano (acapgalano)"
date: "`r Sys.Date()`"
---

# Overview

This document serves as my In-class Exercise 2 requirement, following the second week of ISSS608 VAA lecture of Professor Kam on January 21, 2023.

## Tidyverse

`Tidyverse` is a collection of packages that (as named) is used to **tidy data** in the field of data analytics. The `tidyverse` packages and workflow are shown below.

[![Figure taken from \[Hands-on Exercise 1 slides of ISSS608 course page\](https://isss608-ay2022-23jan.netlify.app/hands-on_ex/hands-on_ex01/hands-on_ex01-ggplot2#/4)](images/image-244973283.png){fig-align="center" width="545"}](https://isss608-ay2022-23jan.netlify.app/hands-on_ex/hands-on_ex01/hands-on_ex01-ggplot2#/4)

In this In-class Exercise, we make use of tidyverse, especially the included package `ggplot2` to explore the different graphics that can be designed and how they can be customized.

## The Data

The data consists of exam scores of students from different classes for different subjects, namely,

# Getting Started

## Loading the required packages

The function `p_load()` from **`pacman`** checks if inputted packages are already installed. If they are, they are loaded into the R environment. Otherwise, they are installed then loaded in. The code chunk below runs `p_load()` for **`tidyverse`**.

```{r}
pacman::p_load(tidyverse)
```

::: {.callout-note icon="false"}
## 💻 CODE REVIEW!

> Why do we
:::

## Importing the data

The code chunk below uses `read.csv()` to load in the CSV file "*Exam_data.csv*" into the R environment.

```{r}
exam_data <- read.csv("data/Exam_data.csv")
```

## 
