---
title: "In-class Exercise 2: Creating Eelegant Graphics with ggplot2"
---

# Overview

This document serves as my In-class Exercise 2 requirement, following the second week of ISSS608 VAA lecture of Professor Kam on January 21, 2023.

## Tidyverse

`Tidyverse` is a collection of packages that (as named) is used to **tidy data** in the field of data analytics. The `tidyverse` workflow is shown below.

[![Figure taken from [Hands-on Exercise 1 slides of ISSS608 course page](https://isss608-ay2022-23jan.netlify.app/hands-on_ex/hands-on_ex01/hands-on_ex01-ggplot2#/4)](images/image-244973283.png){fig-align="center" width="818"}](https://isss608-ay2022-23jan.netlify.app/hands-on_ex/hands-on_ex01/hands-on_ex01-ggplot2#/4)

In this In-class Exercise, we make use of tidyverse, especially the included package `ggplot2` to explore the different graphics that can be designed and how they can be customized.

## The Scenario

# Getting Started

## Loading the required packages

The function `p_load()` from **`pacman`** checks if inputted packages are already installed. If they are, they are loaded into the R environment. Otherwise, they are installed then loaded in. The code chunk below runs `p_load()` for **`tidyverse`**.

```{r}
pacman::p_load(tidyverse)
```

## Importing the data

```{r}

```

## 
